---
title: "Project_Practical_Machine_Learning"
author: "Vladislav Kaplan"
date: "March 30, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Practical Machine Learning project

Loading packages
```{r}
library(caret); 
library(rattle); 
library(rpart); 
library(rpart.plot)
library(randomForest); 
```

Download Data
```{r}
download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", "pml-training.csv")
download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv", "pml-testing.csv")
```

Clean up and Training/testing set creation
```{r}
Tr <- read.csv("pml-training.csv", na.strings = c("NA", ""))
Ts <- read.csv("pml-testing.csv", na.strings = c("NA", ""))
Tr <- Tr[, colSums(is.na(Tr)) == 0]
Ts <- Ts[, colSums(is.na(Ts)) == 0]
Tr <- Tr[, -c(1:7)]
Ts <- Ts[, -c(1:7)]
```

Validation set creation
```{r}
set.seed(1332) 
inTrain <- createDataPartition(Tr$classe, p = 0.7, list = FALSE)
train <- Tr[inTrain, ]
valid <- Tr[-inTrain, ]
```

Control method definition
```{r}
control <- trainControl(method = "boot", number = 5)
```

Mass non recursive partitioning upproach
```{r}
Model_rpart <- train(classe ~ ., data = train, method = "rpart",trControl = control);
print(Model_rpart,digits=3)
fancyRpartPlot(Model_rpart$finalModel)
```

Stachastic Gradient Boosing upproach
```{r,echo=FALSE}
Model_StochasticGB <- train(classe ~ ., data = train, method = "gbm",trControl = control);
print(Model_StochasticGB,digits=3)
```

Random Forest apporach
```{r}
Model_rf <- train(classe ~ ., data = train, method = "rf", trControl = control);
print(Model_rf, digits = 3)
```


## Predictions on validation set

Mass non recursive partitioning upproach
```{r}
predict_rpart <- predict(Model_rpart, valid)
(conf_rpart <- confusionMatrix(valid$classe, predict_rpart))
```

Stachastic Gradient Boosing upproach
```{r}
predict_Model_StochasticGB <- predict(Model_StochasticGB, valid)
(conf_Model_StochasticGB <- confusionMatrix(valid$classe, predict_Model_StochasticGB))
```

Random Forest apporach
```{r}
predict_rf <- predict(Model_rf, valid)
(conf_rf <- confusionMatrix(valid$classe, predict_rf))
```

## Best predictor on Testing Set
```{r}
(predict(Model_rf, Ts))
```

